\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{url}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning,fit,backgrounds}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

\title{SciRAG-UQ: Uncertainty-Aware Multi-Source Retrieval-Augmented\\
Generation for Scientific Literature Synthesis}

\author{
\IEEEauthorblockN{Kaushal Rao G}
\IEEEauthorblockA{
\textit{Department of Artificial Intelligence \& Data Science}\\
\textit{Amrita Vishwa Vidyapeetham, Coimbatore, India}\\
kaushalrog@gmail.com
}
}

\maketitle

%% ─────────────────────────────────────────────────────────────────────────────
\begin{abstract}
Retrieval-Augmented Generation (RAG) has emerged as the dominant paradigm for
grounding large language model (LLM) outputs in external knowledge. However,
existing RAG systems lack principled mechanisms for quantifying \emph{when} to
trust a generated answer --- a critical gap in high-stakes scientific literature
synthesis. We present \textbf{SciRAG-UQ}, a multi-source RAG framework that
integrates three complementary uncertainty signals: (1) retrieval confidence from
hybrid dense--sparse retrieval, (2) generation entropy derived from token-level
log-probabilities, and (3) semantic consistency across alternate generations.
These signals are fused into a composite confidence score that drives an
adaptive abstention policy, allowing the system to withhold answers when evidence
is insufficient. Evaluated on a curated benchmark of 500 scientific questions
spanning factual, comparative, and unanswerable categories, SciRAG-UQ achieves
\textbf{faithfulness of 0.847}, \textbf{abstention precision of 0.912}, and
reduces hallucination rate by \textbf{38.6\%} compared to a vanilla RAG baseline,
while maintaining an Expected Calibration Error (ECE) of 0.043. Code and
benchmark are released at \url{https://github.com/kaushalrog/scirag-uq}.
\end{abstract}

\begin{IEEEkeywords}
Retrieval-Augmented Generation, Uncertainty Quantification, Scientific NLP,
Hallucination Detection, Abstention, Big Data, Large Language Models
\end{IEEEkeywords}

%% ─────────────────────────────────────────────────────────────────────────────
\section{Introduction}
\label{sec:intro}

The proliferation of scientific literature has reached unprecedented scale:
arXiv alone hosts over 2.3 million papers, with more than 15,000 new submissions
monthly \cite{arxiv2024}. Researchers increasingly rely on AI-assisted tools to
navigate this corpus, yet current systems suffer from a fundamental
problem: they generate plausible-sounding answers regardless of whether
supporting evidence exists in the retrieved context --- the hallucination problem
\cite{maynez2020faithfulness, ji2023survey}.

Retrieval-Augmented Generation (RAG) \cite{lewis2020rag} partially mitigates
hallucination by conditioning generation on retrieved documents. However, vanilla
RAG provides no confidence signal to the end user, and no mechanism to abstain
when retrieved evidence is weak or contradictory. This is particularly dangerous
in scientific literature synthesis, where a fabricated citation or a misattributed
result can have serious downstream consequences.

\textbf{Our contributions} are:
\begin{itemize}
    \item A multi-signal uncertainty quantification (UQ) framework for RAG
          combining retrieval confidence, generation entropy, and semantic
          consistency (Section~\ref{sec:method}).
    \item A cascaded abstention policy that withholds answers when composite
          confidence falls below a calibrated threshold (Section~\ref{sec:method}).
    \item Hybrid dense--sparse retrieval with Maximal Marginal Relevance
          (MMR) re-ranking for diverse, non-redundant context windows
          (Section~\ref{sec:method}).
    \item A benchmark of 500 annotated scientific QA items spanning four
          difficulty categories, including deliberately unanswerable questions
          (Section~\ref{sec:experiments}).
    \item Empirical analysis demonstrating that uncertainty-aware abstention
          significantly reduces hallucination while preserving answer quality
          on answerable questions (Section~\ref{sec:results}).
\end{itemize}

%% ─────────────────────────────────────────────────────────────────────────────
\section{Related Work}
\label{sec:related}

\subsection{Retrieval-Augmented Generation}
Lewis et al.\ \cite{lewis2020rag} introduced RAG as a non-parametric memory
extension for sequence-to-sequence models. Subsequent work scaled RAG to
larger corpora \cite{izacard2021leveraging} and introduced iterative retrieval
strategies \cite{shao2023iterative}. Self-RAG \cite{asai2023selfrag} introduced
reflection tokens to guide retrieval decisions, most closely related to our work,
but does not provide calibrated confidence scores.

\subsection{Uncertainty Quantification in LLMs}
Kadavath et al.\ \cite{kadavath2022language} showed that LLMs can be calibrated
to estimate their own correctness. Kuhn et al.\ \cite{kuhn2023semantic}
introduced semantic entropy as a generation uncertainty measure over
semantically equivalent answer clusters. Xiong et al.\ \cite{xiong2023llms}
benchmarked multiple UQ methods and found that hybrid approaches outperform
single-signal methods. Our work differs in applying UQ explicitly to the RAG
pipeline and combining retrieval-side signals with generation-side entropy.

\subsection{Hallucination Detection}
Manakul et al.\ \cite{manakul2023selfcheckgpt} proposed SelfCheckGPT for
detecting hallucinations via consistency across stochastic samples. RAGAS
\cite{es2023ragas} introduced a suite of reference-free evaluation metrics
for RAG. We extend these concepts with an online abstention mechanism that
operates at inference time without requiring multiple model calls.

%% ─────────────────────────────────────────────────────────────────────────────
\section{Methodology}
\label{sec:method}

\subsection{System Architecture}

Figure~\ref{fig:arch} presents the SciRAG-UQ pipeline. At inference time,
a user query flows through six sequential stages: (1) multi-source ingestion,
(2) hybrid retrieval, (3) context assembly, (4) LLM generation, (5) uncertainty
estimation, and (6) abstention decision.

\begin{figure}[!t]
\centering
\begin{tikzpicture}[
    box/.style={rectangle, rounded corners=3pt, draw=blue!50!black,
                fill=blue!10, minimum width=2.2cm, minimum height=0.7cm,
                font=\small, text centered},
    uqbox/.style={rectangle, rounded corners=3pt, draw=orange!70!black,
                  fill=orange!15, minimum width=2.2cm, minimum height=0.7cm,
                  font=\small, text centered},
    arr/.style={->, thick, blue!60!black},
    node distance=0.5cm
]
    \node[box] (Q) {User Query};
    \node[box, below=of Q] (R) {Hybrid Retriever\\(Dense + BM25)};
    \node[box, below=of R] (C) {Context Builder\\(MMR Re-rank)};
    \node[box, below=of C] (G) {LLM Generation\\(Groq / Llama 3.1)};
    \node[uqbox, right=1.2cm of R] (UQ1) {Retrieval\\Confidence};
    \node[uqbox, right=1.2cm of G] (UQ2) {Generation\\Entropy};
    \node[uqbox, below=0.3cm of UQ2] (UQ3) {Semantic\\Consistency};
    \node[uqbox, below=0.5cm of UQ1, xshift=0.6cm] (COMP) {Composite\\Confidence};
    \node[box, below=of G] (ABS) {Abstention\\Policy};
    \node[box, below=of ABS] (OUT) {Answer + UQ Score};

    \draw[arr] (Q) -- (R);
    \draw[arr] (R) -- (C);
    \draw[arr] (C) -- (G);
    \draw[arr] (G) -- (ABS);
    \draw[arr] (ABS) -- (OUT);
    \draw[arr] (R) -- (UQ1);
    \draw[arr] (G) -- (UQ2);
    \draw[arr] (UQ1) -- (COMP);
    \draw[arr] (UQ2) -- (COMP);
    \draw[arr] (UQ3) -- (COMP);
    \draw[arr] (COMP) -- (ABS);
\end{tikzpicture}
\caption{SciRAG-UQ architecture. Uncertainty signals from both retrieval
and generation stages are fused into a composite confidence score that
drives the abstention policy.}
\label{fig:arch}
\end{figure}

\subsection{Multi-Source Ingestion}

SciRAG-UQ ingests papers from two sources: the arXiv API and the Semantic Scholar
Academic Graph (S2AG). For each paper, we extract structured text using PyMuPDF
with a heuristic section boundary detector that identifies standard academic
sections (Abstract, Introduction, Related Work, etc.). Semantic Scholar enriches
each record with citation counts and TLDR summaries, providing quality signals
for source weighting.

\subsection{Hybrid Retrieval with MMR}

Given query $q$, we retrieve a candidate pool of $k_c = k \cdot m$ chunks
(where $m=3$ is the candidate multiplier) using dense retrieval via ChromaDB's
HNSW index. Let $s_d(q, d_i)$ be the cosine similarity between query and
document embeddings. Sparse BM25 scores $s_{bm25}(q, d_i)$ are computed over
the same candidate pool. The hybrid score is:

\begin{equation}
s_h(q, d_i) = \alpha \cdot s_d(q, d_i) + (1 - \alpha) \cdot s_{bm25}(q, d_i)
\label{eq:hybrid}
\end{equation}

where $\alpha = 0.7$ is the dense weight, determined by grid search on the
validation split. MMR re-ranking then selects the final top-$k$ chunks:

\begin{equation}
\text{MMR}(d_i) = \lambda \cdot s_d(q, d_i)
                 - (1-\lambda) \cdot \max_{d_j \in \mathcal{S}} s_d(d_i, d_j)
\label{eq:mmr}
\end{equation}

where $\mathcal{S}$ is the set of already-selected chunks and $\lambda = 0.5$.

\subsection{Uncertainty Quantification}
\label{sec:uq}

We compute three uncertainty signals:

\subsubsection{Retrieval Confidence}
The retrieval confidence is the mean hybrid score over the top-$k$ retrieved
chunks:
\begin{equation}
C_r = \frac{1}{k} \sum_{i=1}^{k} s_h(q, d_i)
\label{eq:ret_conf}
\end{equation}

\subsubsection{Generation Entropy}
Given token-level log-probabilities $\{p_t\}$ from the LLM, we compute the
mean entropy over the top-$V$ logprob distribution at each token position $t$:
\begin{equation}
H_t = -\sum_{v=1}^{V} \tilde{p}_{tv} \log \tilde{p}_{tv}, \quad
C_g = \frac{1}{1 + \bar{H}}
\label{eq:entropy}
\end{equation}
where $\tilde{p}_{tv}$ are normalised probabilities and $\bar{H}$ is the mean
entropy across all tokens. This follows the formulation of \cite{kuhn2023semantic}.

\subsubsection{Semantic Consistency}
For optional multi-sample consistency (disabled in latency-sensitive deployments),
we compute the mean pairwise cosine similarity between the primary answer embedding
and $n_s$ alternate answer embeddings:
\begin{equation}
C_s = \frac{1}{n_s} \sum_{j=1}^{n_s} \cos(\mathbf{e}_0, \mathbf{e}_j)
\label{eq:consistency}
\end{equation}

\subsubsection{Composite Confidence}
The three signals are combined as a weighted sum:
\begin{equation}
C_{comp} = w_r C_r + w_g C_g + w_s C_s
\label{eq:composite}
\end{equation}
where $(w_r, w_g, w_s) = (0.40, 0.35, 0.25)$, tuned via grid search on a
held-out validation set of 100 items.

\subsection{Cascaded Abstention Policy}

Rather than a single threshold on $C_{comp}$, we apply a cascade that checks
signals in priority order (retrieval $\rightarrow$ coverage $\rightarrow$
entropy $\rightarrow$ consistency $\rightarrow$ composite). Abstention at any
stage short-circuits the remaining checks:

\begin{algorithm}
\caption{CascadeAbstention}
\label{alg:abstain}
\begin{algorithmic}[1]
\REQUIRE UQ metrics $\mathbf{u}$, thresholds $\boldsymbol{\tau}$
\IF{$C_r < \tau_r$} \RETURN \textsc{Abstain}(low\_retrieval) \ENDIF
\IF{$\text{coverage} < \tau_{cov}$} \RETURN \textsc{Abstain}(low\_coverage) \ENDIF
\IF{$\bar{H} > \tau_H$} \RETURN \textsc{Abstain}(high\_entropy) \ENDIF
\IF{$C_s < \tau_s$} \RETURN \textsc{Abstain}(low\_consistency) \ENDIF
\IF{$C_{comp} < \tau_{comp}$} \RETURN \textsc{Abstain}(low\_composite) \ENDIF
\RETURN \textsc{Answer}
\end{algorithmic}
\end{algorithm}

%% ─────────────────────────────────────────────────────────────────────────────
\section{Experiments}
\label{sec:experiments}

\subsection{Corpus Construction}

We ingested 512 papers from arXiv covering the topics of RAG, LLMs, knowledge
graphs, and scientific NLP (query terms: \texttt{retrieval augmented generation},
\texttt{LLM uncertainty}, \texttt{scientific text mining}, \texttt{knowledge
graph question answering}). After deduplication and section extraction, the
corpus comprises 47,382 text chunks (mean 512 characters).

\subsection{Benchmark Dataset}

The BDA-Sci benchmark contains 500 questions in four categories:
\begin{itemize}
    \item \textbf{Factual} (200): Single-hop questions with definite answers
          grounded in the corpus (e.g., ``What architecture does [paper X] use?'').
    \item \textbf{Comparative} (100): Multi-document comparison questions
          requiring synthesis across $\geq 2$ papers.
    \item \textbf{Exploratory} (100): Open-ended survey questions
          (e.g., ``What are the main limitations of RAG systems?'').
    \item \textbf{Unanswerable} (100): Questions intentionally outside the
          corpus scope, serving as negative test cases for abstention.
\end{itemize}

Reference answers were written by the authors for factual and comparative
items; unanswerable items carry a ground-truth label of \texttt{truly\_uncertain=True}.

\subsection{Baselines}

We compare SciRAG-UQ against:
\begin{itemize}
    \item \textbf{Vanilla RAG}: Dense-only retrieval, no UQ, no abstention.
    \item \textbf{RAG+Threshold}: Dense retrieval with a simple composite
          confidence threshold (no cascade).
    \item \textbf{Self-RAG} \cite{asai2023selfrag}: Reflection-token guided
          retrieval (reproduced with Llama 3.1 as backbone).
    \item \textbf{SciRAG-UQ (Ours)}: Full system as described.
\end{itemize}

\subsection{Implementation Details}

All experiments use \textbf{Llama 3.1 70B Versatile} via Groq Cloud
(temperature $= 0.1$) for generation, and \texttt{all-MiniLM-L6-v2} for
embeddings (dim $= 384$). ChromaDB with HNSW (cosine space) is used for
vector storage. Cascade thresholds: $\tau_r = 0.35$, $\tau_{cov} = 0.30$,
$\tau_H = 2.8$, $\tau_s = 0.50$, $\tau_{comp} = 0.45$.

%% ─────────────────────────────────────────────────────────────────────────────
\section{Results and Analysis}
\label{sec:results}

\subsection{Main Results}

Table~\ref{tab:main} presents the main evaluation results.

\begin{table}[!t]
\caption{Main Evaluation Results on BDA-Sci Benchmark (500 items)}
\label{tab:main}
\centering
\small
\begin{tabular}{lccccc}
\toprule
\textbf{System} & \textbf{Faith.} & \textbf{Halluc.↓} & \textbf{Abs.P} & \textbf{Abs.R} & \textbf{ECE↓} \\
\midrule
Vanilla RAG         & 0.712 & 0.341 & ---   & ---   & 0.187 \\
RAG+Threshold       & 0.751 & 0.283 & 0.741 & 0.612 & 0.142 \\
Self-RAG            & 0.793 & 0.241 & 0.812 & 0.724 & 0.098 \\
\midrule
\textbf{SciRAG-UQ}  & \textbf{0.847} & \textbf{0.209} & \textbf{0.912} & \textbf{0.883} & \textbf{0.043} \\
\bottomrule
\end{tabular}
\end{table}

SciRAG-UQ achieves the best faithfulness (0.847, +6.8\% over Self-RAG) and
lowest hallucination rate (0.209, $-$38.7\% vs.\ Vanilla RAG). Abstention
precision of 0.912 indicates that when SciRAG-UQ refuses to answer, it is
correct 91.2\% of the time. ECE of 0.043 confirms strong calibration.

\subsection{Ablation Study}

Table~\ref{tab:ablation} shows the contribution of each UQ signal.

\begin{table}[!t]
\caption{Ablation Study — Contribution of Each UQ Signal}
\label{tab:ablation}
\centering
\small
\begin{tabular}{lccc}
\toprule
\textbf{Configuration} & \textbf{Faith.} & \textbf{Halluc.↓} & \textbf{Abs.P} \\
\midrule
No UQ (Vanilla)         & 0.712 & 0.341 & ---   \\
$+C_r$ only             & 0.769 & 0.271 & 0.784 \\
$+C_g$ only             & 0.751 & 0.283 & 0.741 \\
$+C_r + C_g$            & 0.821 & 0.231 & 0.876 \\
$+C_r + C_g + C_s$      & \textbf{0.847} & \textbf{0.209} & \textbf{0.912} \\
\midrule
Cascade vs.\ Threshold  & +0.018 & $-$0.031 & +0.089 \\
MMR vs.\ Top-K          & +0.024 & $-$0.024 & +0.021 \\
\bottomrule
\end{tabular}
\end{table}

Each signal provides complementary gains. The cascade policy provides a
+8.9\% improvement in abstention precision over the simple threshold, confirming
that multi-signal cascades are superior to single-threshold approaches.

\subsection{Confidence Calibration Analysis}

Figure~\ref{fig:calibration} shows the reliability diagram for SciRAG-UQ
versus Vanilla RAG. SciRAG-UQ's confidence scores closely track empirical accuracy
(near-diagonal), while Vanilla RAG is systematically overconfident.

\begin{figure}[!t]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=7cm, height=5.5cm,
    xlabel={Predicted Confidence},
    ylabel={Empirical Accuracy},
    xmin=0, xmax=1, ymin=0, ymax=1,
    xtick={0,0.2,0.4,0.6,0.8,1.0},
    ytick={0,0.2,0.4,0.6,0.8,1.0},
    grid=major, grid style={dashed,gray!30},
    legend pos=south east,
    font=\small,
]
% Perfect calibration diagonal
\addplot[gray, dashed, thick] coordinates {(0,0)(1,1)};
\addlegendentry{Perfect}

% Vanilla RAG — overconfident
\addplot[red, thick, mark=square*] coordinates {
    (0.1,0.08)(0.2,0.14)(0.3,0.20)(0.4,0.29)(0.5,0.35)
    (0.6,0.42)(0.7,0.51)(0.8,0.58)(0.9,0.63)(1.0,0.71)
};
\addlegendentry{Vanilla RAG}

% SciRAG-UQ — well calibrated
\addplot[blue, thick, mark=*] coordinates {
    (0.1,0.09)(0.2,0.21)(0.3,0.29)(0.4,0.41)(0.5,0.49)
    (0.6,0.62)(0.7,0.70)(0.8,0.79)(0.9,0.88)(1.0,0.96)
};
\addlegendentry{SciRAG-UQ (Ours)}
\end{axis}
\end{tikzpicture}
\caption{Reliability diagram. SciRAG-UQ (blue) closely tracks the perfect
calibration diagonal, while Vanilla RAG (red) is systematically overconfident.}
\label{fig:calibration}
\end{figure}

\subsection{Retrieval Ablation: Chunking Strategy}

Semantic chunking (SemanticChunker with $\theta_{sim} = 0.75$) outperforms
recursive character splitting on comparative and exploratory questions
(faithfulness: 0.847 vs.\ 0.819), while recursive chunking is faster
(1.4$\times$). We use recursive chunking as the default with semantic chunking
as an optional high-quality mode.

%% ─────────────────────────────────────────────────────────────────────────────
\section{Discussion}

\subsection{When Does Abstention Help Most?}

Qualitative analysis reveals three dominant abstention triggers:
(a) questions about papers not in the corpus (unanswerable, 78\% of abstentions),
(b) questions requiring numerical reasoning beyond the model's grasp (15\%),
(c) contradictory evidence across sources (7\%).
The cascade policy correctly identifies all three categories through different
signal combinations, validating the multi-signal design.

\subsection{Limitations}

\textbf{Logprob availability}: Generation entropy requires token-level
log-probabilities from the LLM provider. Not all hosted models expose this.
We fall back to a neutral prior ($C_g = 0.8$) when unavailable.
\textbf{Consistency overhead}: Semantic consistency with $n_s = 3$ requires
3$\times$ generation calls, tripling latency. We disable it by default and
recommend it only for high-stakes queries.
\textbf{Corpus coverage}: SciRAG-UQ is only as good as its corpus.
Gaps in coverage are a root cause of unanswerable questions; expanding
the corpus is the primary recommendation for improving recall.

\subsection{Reproducibility}

All code, the BDA-Sci benchmark, and configuration files are publicly available
at \url{https://github.com/kaushalrog/scirag-uq}. Experiments can be reproduced
with a single \texttt{make eval} command given a Groq API key.

%% ─────────────────────────────────────────────────────────────────────────────
\section{Conclusion}

We presented SciRAG-UQ, an uncertainty-aware RAG framework for scientific
literature synthesis that combines hybrid retrieval, multi-signal uncertainty
quantification, and cascaded abstention. Our experiments on the BDA-Sci benchmark
demonstrate consistent improvements over baselines across faithfulness,
hallucination rate, calibration error, and abstention quality. We release
all code and benchmarks to facilitate reproducibility and future work.

Future directions include: (1) fine-tuning the embedding model on scientific
domain text; (2) cross-lingual extension; (3) graph-based retrieval augmenting
vector search with citation network structure.

%% ─────────────────────────────────────────────────────────────────────────────
\bibliographystyle{IEEEtran}
\begin{thebibliography}{99}

\bibitem{lewis2020rag}
P.~Lewis, E.~Perez, A.~Piktus et al., ``Retrieval-augmented generation for
knowledge-intensive NLP tasks,'' in \textit{Proc. NeurIPS}, 2020.

\bibitem{asai2023selfrag}
A.~Asai, Z.~Wu, Y.~Wang, A.~Sil, and H.~Hajishirzi, ``Self-RAG: Learning to
retrieve, generate, and critique through self-reflection,'' in
\textit{Proc. ICLR}, 2024.

\bibitem{kuhn2023semantic}
L.~Kuhn, Y.~Gal, and S.~Farquhar, ``Semantic uncertainty: Linguistic
invariances for uncertainty estimation in natural language generation,'' in
\textit{Proc. ICLR}, 2023.

\bibitem{kadavath2022language}
S.~Kadavath, T.~Conerly, A.~Askell et al., ``Language models (mostly) know
what they know,'' \textit{arXiv:2207.05221}, 2022.

\bibitem{es2023ragas}
S.~Es, J.~James, L.~Espinosa-Anke, and S.~Schockaert, ``RAGAS: Automated
evaluation of retrieval augmented generation,'' \textit{arXiv:2309.15217},
2023.

\bibitem{manakul2023selfcheckgpt}
P.~Manakul, A.~Liusie, and M.~J.~F.~Gales, ``SelfCheckGPT: Zero-resource
black-box hallucination detection for generative large language models,'' in
\textit{Proc. EMNLP}, 2023.

\bibitem{izacard2021leveraging}
G.~Izacard and E.~Grave, ``Leveraging passage retrieval with generative models
for open domain question answering,'' in \textit{Proc. EACL}, 2021.

\bibitem{shao2023iterative}
Z.~Shao, Y.~Gong, Y.~Shen et al., ``Enhancing retrieval-augmented large
language models with iterative retrieval-generation synergy,''
\textit{arXiv:2305.15294}, 2023.

\bibitem{maynez2020faithfulness}
J.~Maynez, S.~Narayan, B.~Bohnet, and R.~McDonald, ``On faithfulness and
factuality in abstractive summarization,'' in \textit{Proc. ACL}, 2020.

\bibitem{ji2023survey}
Z.~Ji, N.~Lee, R.~Frieske et al., ``Survey of hallucination in natural
language generation,'' \textit{ACM Comput. Surv.}, vol.~55, no.~12, 2023.

\bibitem{xiong2023llms}
M.~Xiong, Z.~Hu, X.~Lu et al., ``Can LLMs express their uncertainty? An
empirical evaluation of confidence elicitation in LLMs,''
\textit{arXiv:2306.13063}, 2023.

\bibitem{arxiv2024}
arXiv.org, ``arXiv statistics,'' 2024. [Online]. Available:
\url{https://arxiv.org/stats/main}

\end{thebibliography}

\end{document}
